Constructing the transition graphs of interacting hysterons

### 2022-05-31 SI_design_ineqs.tex
Reworked piece on design inequalities using new definitions

We can then rewrite the conditions from Equation \ref{eq:dynamics} into a single statement: 

@@

As described in Section \ref{sec:constructing_graphs}, the graph in Fig. \ref{fig:design_ineqs_example} can be broken down as the combination of a base graph and the avalanche $11\downarrow 10 \downarrow 00$. In the same way, we can distinguish two parts to the design inequalities. One one hand, for each transition there is a set of inequalities required to initiate the transition, which is of the form

@@

    U_i^+(S^{(0)} = \min_{s_j = 0}U_j^+(S^{(0)})

@@

or 

@@

    U_i-(S^{(0)} = \max_{s_j = 1}U_j^-(S^{(0)})

@@

The set of inequalities required to initiate the transition is associated with the base graph, and we refer to it accordingly as the base inequalities. On the other hand, for each transition there are $l$ sets of inequalities describing the stability of subsequent states under the field that initiated the transition. We refer to the part of the design inequalities that describes the stability as the relaxation inequalities.\\
For the general model where the switching fields $u_i^{+, -}(S)$ are independent, we note that the base inequalities are always solvable. This is because there is no overlap between the sets of inequalities for the individual transitions, since they describe relations between switching fields at the same state $S^{(0)}$. In contrast, the relaxation inequalities describe relations between switching fields at different states, so that it is possible for a combination of transitions to be incompatible even in the general model.\\

>>>>

We can then rewrite the conditional statement from Equation \ref{eq:dynamics} into a single statement: 

@@

We can generalize the method for finding the design inequalities to any transition path $S^{(0)}\rightarrow S^{(1)}\rightarrow ... \rightarrow S^{(1)}$. One one hand, for each transition there is a set of inequalities required to initiate the transition, which is of the form

@@

    U_i^+(S) &= \min_{s_j=0}U_j^+(S), s_i=0\\
     U_i^-(S)&=\max_{s_j=1}U_j^-(S), s_i=1\\

@@

which we can shorten as:

@@

r_iU_i(S) = \min_{s_j=s_i}r_jU_j(S)

@@

where $i$ is the hysteron that flips. We refer to the set of inequalities that is required to initiate the transition as the base inequalities.\\
Let us now define the field $U_i(S^{(0)}$ which initiates the transition as $U*$. On top of the base inequalities, an an additional set of linear inequalities is needed to describe the stability of each of the states $S^{(1)}, ..., S^{(l)}$ under $U*$. For the final state $S^{(l)}$, all hysterons must be stable, so that:
r_jU_j(S^{(l)}) > r_jU* \forall j
For the intermediate states $S^{(1)}, ..., S^{(l-1)}$, all hysterons are stable except for a single hysteron $k$, for which the inequality flips:
\begin{split}
r_jU_j(S^{(1)}) &> r_jU* \forall j, j \neq k\\
r_kU_k(S^{(1)}) &\leq r_kU*\\
\end{split}
For the general model where the switching fields $U_i^{+, -}(S)$ are independent, we note that the base inequalities are always solvable. This is because there is no overlap between the sets of inequalities for the individual transitions, since they describe relations between switching fields at the same state $S^{(0)}$. In contrast, the relaxation inequalities describe relations between switching fields at different states, so that it is possible for a combination of transitions to be incompatible even in the general model.\\
